A longitudinal analysis of the social information in infants' naturalistic

### 2022-01-07 paper/manuscript/manuscript_dec2021_apa_blinded.Rmd
manual call outs to appendix figures

To address this challenge, we use a modern computer vision model of pose detection to automatically detect the presence of hands and faces from the infant egocentric viewpoint. 
Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints. 
In prior work examining egocentric videos taken from the infant perspective during in-lab play sessions, OpenPose performed comparably to other modern face detection models [@long2021automated].
However, these at-home, naturalistic videos contain more cluttered visual environments, challenging lighting conditions, and many different novel viewpoints.
In this paper, we first validate the use of OpenPose by comparing face and hand detections to a human-annotated set of 24,000 frames. Though OpenPose does not detect faces and hands with perfect accuracy, we find that this model still operates relatively well on these challenging egocentric scenes including multiple people, even if they are partially-occluded (see Figure 1 for example detections and Appendix Figure \ref{fig:error_examples} for examples of missed detections and false alarms).

>>>>

To address this challenge, we use a modern computer vision model of pose detection to automatically detect the presence of hands and faces from the infant egocentric viewpoint. 
Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints. 
In prior work examining egocentric videos taken from the infant perspective during in-lab play sessions, OpenPose performed comparably to other modern face detection models [@long2021automated].
However, these at-home, naturalistic videos contain more cluttered visual environments, challenging lighting conditions, and many different novel viewpoints.
In this paper, we first validate the use of OpenPose by comparing face and hand detections to a human-annotated set of 24,000 frames. Though OpenPose does not detect faces and hands with perfect accuracy, we find that this model still operates relatively well on these challenging egocentric scenes including multiple people, even if they are partially-occluded (see Figure 1 for example detections and Appendix Figure A1 for examples of missed detections and false alarms).
